Computer Science House Constitution

### 2023-10-29 constitution.tex
Resolve #94 Remove list of directors (#121)
* Removed list of directors

* Added bullet point in responsibilities of each voting member stating that they can vote
Fixed wording (#118)

\asection{Active Membership}
\asubsection{Active Membership Qualifications}
Active Membership is open to all students currently enrolled at the Rochester Institute of Technology who have passed the Introductory Evaluation and their most recent Membership Evaluation.
\asubsection{Active Membership Selection}
Alumni Members in good standing may self-select into Active Membership by paying dues to the Financial Director and notifying the Evaluations Director.
\\*\\*
Any Alumni Member in bad standing (\ref{Alumni Membership Selection}) may become an Active Member by notifying the Evaluations Director of their intent to participate, who will bring them up for a Simple Majority vote at the next House meeting.
If the vote passes the Alumni is reinstated as an Active Member with Off-Floor status effective immediately.
\asubsection{Active Membership Expectations}
Active members are expected to be active participants in the House as defined in \ref{Expectations of House Members}.
\asubsection{Active Membership Privileges}
Active Members receive the right to:
\begin{itemize}
	\item Vote on all issues brought before the House
	\item Reside on the House
	\item Hold an Executive Board office on the House
	\item Use Computer Science House facilities
	\item Attend Computer Science House functions
	\item Receive priority for available housing on the House when returning from cooperative education
	\item Guaranteed housing in compliance with the Residence Life policies regarding Special Interest Houses and the Housing Selection Process (if they have On-Floor status)
\end{itemize}
Active Members currently on co-op forfeit their right to vote on house issues, and likewise do not count towards quorum.
Exceptions may be made at the discretion of the Evaluations Director.
\asubsection{Active Membership Evaluations}
Active Members are evaluated annually through the Evaluation Process as described in \ref{Evaluations Processes}.
\asubsection{Active Membership Leave of Absence}
An Active member may at any time request a leave of absence using the process described in \ref{Leave of Absence}.
For the duration of an absence, a member:
\begin{itemize}
	\item Forfeits their right to vote
	\item Does not count towards quorum
	\item Will not be required to attend House Meeting
\end{itemize}
\asubsection{Active Membership Resignations}
An Active member may resign by submitting, in writing, the reason for resignation to the Chairperson, or Evaluations Director.
Instead of forfeiting membership, Active members who resign may elect to become Alumni defined in \ref{Alumni Membership Selection}.
The resignation will take effect immediately and an announcement will be made at the following House Meeting.
\asubsection{Active Membership Term}
Active Membership shall last until the member resigns or changes membership status.

@@

% ARTICLE V - EXECUTIVE BOARD
\article{Executive Board}
The Executive Board is the main governing body of the House.
Its purpose is to provide leadership and direction for the House, to oversee the day-to-day operations of the House, and to initiate and organize programs and projects for the House.
It is composed of the seven permanent directors and the Chairperson.
\\*\\*
There is one permanent directorship for each major aspect of the government of the House and each one is chaired by an Executive Board member.
Ad Hoc directorships are created on an as-needed basis.
They are generally very task oriented and are chaired by a House member.
A directorship has some jurisdiction in its area of interest and often is responsible for the day-to-day decisions regarding its area of interest.
Any large expenditures or large effect decisions must be brought before the entire House
\asection{Members of the Executive Board}
\asubsection{Voting Members}
\begin{itemize}
	\item Evaluations Director
	\item Social Director(s)
	\item Financial Director
	\item Research and Development Director(s)
	\item House Improvements Director
	\item Operational Communications Director
	\item House History Director
	\item Public Relations Director
\end{itemize}
\asubsection{Non-Voting Members}
\begin{itemize}
	\item Chairperson
	\item House Secretary
	\item Ad Hoc Director(s)
\end{itemize}

\asection{Responsibilities}
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
\asubsection{Responsibilities of the Executive Board}
\begin{enumerate}
	\item To hold a weekly meeting specific to their responsibilities and submit notes to the House
	\item To meet, as an Executive Board, at least weekly during the Standard Operating Session, as defined in \ref{Standard Operating Session} to discuss and report the operations of the House
	\item To report pertinent information to House members at the following House Meeting
	\item To maintain records of the goals defined by each previous Executive Board
	\item To act as a Judicial Board as defined in \ref{Judicial}
	\item To review major projects, as defined in \ref{Expectations of House Members}
	\item To make the final vote regarding conditionals and appeals as defined in \ref{Membership Evaluation}
	\item To respect the privacy of House Members confiding in the Executive Board, barring situations related to sexual assault or endangerment of oneself or others
	\item To publish a document at the end of each semester to all Members stating House’s accomplishments of that semester
	\item To review and update the Constitution at the end of each Standard Operating Session, as defined in \ref{Standard Operating Session}.
		The constitution should remain up to date with current practices.
\end{enumerate}

@@

\asubsection{Responsibilities of the Evaluations Director}
\begin{enumerate}
	\item To preside over Evaluations Meetings
	\item To exercise general supervision over Evaluations operations
	\item To oversee the screening, interviewing, and acceptance or rejection of prospective House members
	\item To oversee the Semi-Annual Evaluations of current House members
	\item To collaborate with the Residence Life Advisor to determine room change selection and any changes of membership residency
	\item To act as a part of a Judicial Board as defined in \ref{Judicial}
	\item To prepare the House for Open Houses, tours, and special events
\end{enumerate}

\asubsection{Responsibilities of the Social Director}
\begin{enumerate}
	\item To preside over Social Meetings in which House members are encouraged to bring ideas for social events
	\item To exercise general supervision over Social operations
	\item To oversee the organization, initiation, and execution of House activities and events
	\item To ensure that there is a variety of activities for House members to participate in throughout the academic year
\end{enumerate}

\asubsection{Responsibilities of the Public Relations Director}
\begin{enumerate}
	\item To preside over Public Relations Directorship Meetings
	\item To operate House social media accounts intended to represent House as a whole
	\item To oversee the organization, initiation, and execution of House philanthropic events
	\item To preserve and improve the public image of House
	\item To collaborate with other Executive Board members to organize, initiate, execute, and advertise any events that are intended to be attended by persons whom have never been Active Members

@@

\asubsection{Responsibilities of the Financial Director}
\begin{enumerate}
	\item To preside over Financial Meetings in which House members are encouraged to bring ideas for fund-raising activities
	\item To supervise financial administrators and transactions involving house projects
	\item To maintain financial and inventory records of House capital and assets
	\item To plan and enforce a House budget
	\item To oversee House finances and generation of House funds
	\item To publish a semesterly House financial statement
	\item To supervise the collection of semesterly House dues
	\item To oversee the planning and execution of fundraising events
\end{enumerate}

\asubsection{Responsibilities of the Research and Development Director}
\begin{enumerate}
	\item To preside over Research and Development Meetings in which House members are encouraged to bring ideas for projects
	\item To exercise general supervision over Research and Development operations
	\item To oversee the planning, organization and construction of technical projects for the House's benefit
	\item To collaborate with the Operational Communications Director in an attempt to fulfill the House's need for technical equipment
	\item To provide seminars and tutorials to educate House members in technical areas
\end{enumerate}

\asubsection{Responsibilities of the House Improvements Director}
\begin{enumerate}
	\item To preside over House Improvements Meetings
	\item To exercise general supervision over the House Improvements operations
	\item To oversee the organization and construction of physical improvements to the House
	\item To oversee the general maintenance of the appearance of the House
\end{enumerate}

\asubsection{Responsibilities of the Operational Communications Director}
\begin{enumerate}
	\item To represent the Root Type Persons at Executive Board Meetings and at House Meetings
	\item To report the status of the House computer systems and network to the Executive Board and House members
\end{enumerate}

\asubsection{Responsibilities of the House History Director}
\begin{enumerate}
	\item To preside over House History Meetings
	\item To exercise general supervision over the House History operations
	\item To maintain, uphold, and promote house traditions
	\item To collaborate with the Social Director(s) to ensure that all the Active, Alumni, and Advisory Members are informed of upcoming events
	\item To oversee the production and distribution of a semi-annual newsletter
	\item To oversee the creation of a yearbook outlining House events for the year
\end{enumerate}

>>>>

\asection{Active Membership}
\asubsection{Active Membership Qualifications}
Active Membership is open to all students currently enrolled at the Rochester Institute of Technology who have passed the Introductory Evaluation and their most recent Membership Evaluation.
\asubsection{Active Membership Selection}
Alumni Members in good standing may self-select into Active Membership by paying dues to the Financial Director and notifying the Evaluations Director.
\\*\\*
Any Alumni Member in bad standing (\ref{Alumni Membership Selection}) may become an Active Member by notifying the Evaluations Director of their intent to participate, who will bring them up for a Simple Majority vote at the next House meeting.
If the vote passes the Alumni is reinstated as an Active Member with Off-Floor status effective immediately.
\asubsection{Active Membership Expectations}
Active members are expected to be active participants in the House as defined in \ref{Expectations of House Members}.
\asubsection{Active Membership Privileges}
Active Members receive the privilege to:
\begin{itemize}
	\item Vote on all issues brought before the House
	\item Reside on the House
	\item Hold an Executive Board office on the House
	\item Use Computer Science House facilities
	\item Attend Computer Science House functions
	\item Receive priority for available housing on the House when returning from cooperative education
	\item Guaranteed housing in compliance with the Residence Life policies regarding Special Interest Houses and the Housing Selection Process (if they have On-Floor status)
\end{itemize}
Active Members currently on co-op forfeit their right to vote on house issues, and likewise do not count towards quorum.
Exceptions may be made at the discretion of the Evaluations Director.
\asubsection{Active Membership Evaluations}
Active Members are evaluated annually through the Evaluation Process as described in \ref{Evaluations Processes}.
\asubsection{Active Membership Leave of Absence}
An Active member may at any time request a leave of absence using the process described in \ref{Leave of Absence}.
For the duration of an absence, a member:
\begin{itemize}
	\item Forfeits their right to vote
	\item Does not count towards quorum
	\item Will not be required to attend House Meeting
\end{itemize}
\asubsection{Active Membership Resignations}
An Active member may resign by submitting, in writing, the reason for resignation to the Chairperson, or Evaluations Director.
Instead of forfeiting membership, Active members who resign may elect to become Alumni defined in \ref{Alumni Membership Selection}.
The resignation will take effect immediately and an announcement will be made at the following House Meeting.
\asubsection{Active Membership Term}
Active Membership shall last until the member resigns or changes membership status.

@@

% ARTICLE V - EXECUTIVE BOARD
\article{Executive Board}
The Executive Board is the main governing body of the House.
Its purpose is to provide leadership and direction for the House, to oversee the day-to-day operations of the House, and to initiate and organize programs and projects for the House.
It is composed of the seven permanent directors and the Chairperson.
\\*\\*
There is one permanent directorship for each major aspect of the government of the House and each one is chaired by an Executive Board member.
Ad Hoc directorships are created on an as-needed basis.
They are generally very task oriented and are chaired by a House member.
A directorship has some jurisdiction in its area of interest and often is responsible for the day-to-day decisions regarding its area of interest.
Any large expenditures or large effect decisions must be brought before the entire House

\asection{Responsibilities}

\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
\asubsection{Responsibilities of the Executive Board}
\begin{enumerate}
	\item To hold a weekly meeting specific to their responsibilities and submit notes to the House
	\item To meet, as an Executive Board, at least weekly during the Standard Operating Session, as defined in \ref{Standard Operating Session} to discuss and report the operations of the House
	\item To report pertinent information to House members at the following House Meeting
	\item To maintain records of the goals defined by each previous Executive Board
	\item To act as a Judicial Board as defined in \ref{Judicial}
	\item To review major projects, as defined in \ref{Expectations of House Members}
	\item To make the final vote regarding conditionals and appeals as defined in \ref{Membership Evaluation}
	\item To respect the privacy of House Members confiding in the Executive Board, barring situations related to sexual assault or endangerment of oneself or others
	\item To publish a document at the end of each semester to all Members stating House’s accomplishments of that semester
	\item To review and update the Constitution at the end of each Standard Operating Session, as defined in \ref{Standard Operating Session}.
		The constitution should remain up to date with current practices.
\end{enumerate}

@@

\asubsection{Responsibilities of the Evaluations Director}
\begin{enumerate}
	\item To preside over Evaluations Meetings
	\item To exercise general supervision over Evaluations operations
	\item To oversee the screening, interviewing, and acceptance or rejection of prospective House members
	\item To oversee the Semi-Annual Evaluations of current House members
	\item To collaborate with the Residence Life Advisor to determine room change selection and any changes of membership residency
	\item To act as a part of a Judicial Board as defined in \ref{Judicial}
	\item To prepare the House for Open Houses, tours, and special events
	\item To vote on issues presented to the Executive Board
\end{enumerate}

\asubsection{Responsibilities of the Social Director(s)}
\begin{enumerate}
	\item To preside over Social Meetings in which House members are encouraged to bring ideas for social events
	\item To exercise general supervision over Social operations
	\item To oversee the organization, initiation, and execution of House activities and events
	\item To ensure that there is a variety of activities for House members to participate in throughout the academic year
	\item To vote on issues presented to the Executive Board
\end{enumerate}

\asubsection{Responsibilities of the Public Relations Director}
\begin{enumerate}
	\item To preside over Public Relations Directorship Meetings
	\item To operate House social media accounts intended to represent House as a whole
	\item To oversee the organization, initiation, and execution of House philanthropic events
	\item To preserve and improve the public image of House
	\item To collaborate with other Executive Board members to organize, initiate, execute, and advertise any events that are intended to be attended by persons whom have never been Active Members
	\item To vote on issues presented to the Executive Board

@@

\asubsection{Responsibilities of the Financial Director}
\begin{enumerate}
	\item To preside over Financial Meetings in which House members are encouraged to bring ideas for fund-raising activities
	\item To supervise financial administrators and transactions involving house projects
	\item To maintain financial and inventory records of House capital and assets
	\item To plan and enforce a House budget
	\item To oversee House finances and generation of House funds
	\item To publish a semesterly House financial statement
	\item To supervise the collection of semesterly House dues
	\item To oversee the planning and execution of fundraising events
	\item To vote on issues presented to the Executive Board
\end{enumerate}

\asubsection{Responsibilities of the Research and Development Director(s)}
\begin{enumerate}
	\item To preside over Research and Development Meetings in which House members are encouraged to bring ideas for projects
	\item To exercise general supervision over Research and Development operations
	\item To oversee the planning, organization and construction of technical projects for the House's benefit
	\item To collaborate with the Operational Communications Director in an attempt to fulfill the House's need for technical equipment
	\item To provide seminars and tutorials to educate House members in technical areas
	\item To vote on issues presented to the Executive Board
\end{enumerate}

\asubsection{Responsibilities of the House Improvements Director}
\begin{enumerate}
	\item To preside over House Improvements Meetings
	\item To exercise general supervision over the House Improvements operations
	\item To oversee the organization and construction of physical improvements to the House
	\item To oversee the general maintenance of the appearance of the House
	\item To vote on issues presented to the Executive Board
\end{enumerate}

\asubsection{Responsibilities of the Operational Communications Director}
\begin{enumerate}
	\item To represent the Root Type Persons at Executive Board Meetings and at House Meetings
	\item To report the status of the House computer systems and network to the Executive Board and House members
	\item To vote on issues presented to the Executive Board
\end{enumerate}

\asubsection{Responsibilities of the House History Director}
\begin{enumerate}
	\item To preside over House History Meetings
	\item To exercise general supervision over the House History operations
	\item To maintain, uphold, and promote house traditions
	\item To collaborate with the Social Director(s) to ensure that all the Active, Alumni, and Advisory Members are informed of upcoming events
	\item To oversee the production and distribution of a semi-annual newsletter
	\item To oversee the creation of a yearbook outlining House events for the year
	\item To vote on issues presented to the Executive Board
\end{enumerate}
